---
title: "Mini Data Analysis Milestone 2"
output: github_document
---

*To complete this milestone, you can either edit [this `.rmd` file](https://raw.githubusercontent.com/UBC-STAT/stat545.stat.ubc.ca/master/content/mini-project/mini-project-2.Rmd) directly. Fill in the sections that are commented out with `<!--- start your work here--->`. When you are done, make sure to knit to an `.md` file by changing the output in the YAML header to `github_document`, before submitting a tagged release on canvas.*

# Welcome to the rest of your mini data analysis project!

In Milestone 1, you explored your data. and came up with research questions. This time, we will finish up our mini data analysis and obtain results for your data by: 

- Making summary tables and graphs 
- Manipulating special data types in R: factors and/or dates and times.
-   Fitting a model object to your data, and extract a result.
-   Reading and writing data as separate files.

We will also explore more in depth the concept of *tidy data.* 

**NOTE**: The main purpose of the mini data analysis is to integrate what you learn in class in an analysis. Although each milestone provides a framework for you to conduct your analysis, it's possible that you might find the instructions too rigid for your data set. If this is the case, you may deviate from the instructions -- just make sure you're demonstrating a wide range of tools and techniques taught in this class.

# Instructions

**To complete this milestone**, edit [this very `.Rmd` file](https://raw.githubusercontent.com/UBC-STAT/stat545.stat.ubc.ca/master/content/mini-project/mini-project-2.Rmd) directly. Fill in the sections that are tagged with `<!--- start your work here--->`.

**To submit this milestone**, make sure to knit this `.Rmd` file to an `.md` file by changing the YAML output settings from `output: html_document` to `output: github_document`. Commit and push all of your work to your mini-analysis GitHub repository, and tag a release on GitHub. Then, submit a link to your tagged release on canvas.

**Points**: This milestone is worth 50 points: 45 for your analysis, and 5 for overall reproducibility, cleanliness, and coherence of the Github submission. 

**Research Questions**: In Milestone 1, you chose two research questions to focus on. Wherever realistic, your work in this milestone should relate to these research questions whenever we ask for justification behind your work. In the case that some tasks in this milestone don't align well with one of your research questions, feel free to discuss your results in the context of a different research question.

# Learning Objectives

By the end of this milestone, you should:

-   Understand what *tidy* data is, and how to create it using `tidyr`.
-   Generate a reproducible and clear report using R Markdown.
-   Manipulating special data types in R: factors and/or dates and times.
-   Fitting a model object to your data, and extract a result.
-   Reading and writing data as separate files.

# Setup

Begin by loading your data and the tidyverse package below:

```{r, message = FALSE}
library(datateachr) # <- might contain the data you picked!
library(tidyverse)
```

# Task 1: Process and summarize your data 

From milestone 1, you should have an idea of the basic structure of your dataset (e.g. number of rows and columns, class types, etc.). Here, we will start investigating your data more in-depth using various data manipulation functions. 

### 1.1 (1 point) 

First, write out the 4 research questions you defined in milestone 1 were. This will guide your work through milestone 2:

<!-------------------------- Start your work below ---------------------------->
**Research Question 1:** What is the relationship between the diameter and their height_range_id in the dataset?

**Research Question 2:** Are certain tree species more prevalent in specific neighborhoods of Vancouver? In other words, are there any relationships between species_name and neighborhood_name?

**Research Question 3:** What is the change of tree population in Vancouver changed over time? In other words, the change in the amount of trees planted each year. (Here, I added a sentence to make the research question more clear to understand.)

**Research Question 4:** What is a change in the tree density of the top 5 most popular tree species in the DOWNTOWN area from 2013 to 2019? 
(This is a newly added question to replace the original research question 1, which is "How does the diameter of trees vary with the corresponding latitude or longitude coordinates in the dataset?" The generated scatter plot of the original Research Question 1 does not seem to yield pretty useful results in terms of the relationship between tree diameter and the corresponding latitude or longitude. Based on the generated graphs, there is no obvious sign that certain longitude or latitude will largely affect the diameter of the trees.)
<!----------------------------------------------------------------------------->

Here, we will investigate your data using various data manipulation and graphing functions.

### 1.2 (8 points)

Now, for each of your four research questions, choose one task from options 1-4 (summarizing), and one other task from 4-8 (graphing). You should have 2 tasks done for each research question (8 total). Make sure it makes sense to do them! (e.g. don't use a numerical variables for a task that needs a categorical variable.). Comment on why each task helps (or doesn't!) answer the corresponding research question.

Ensure that the output of each operation is printed!

Also make sure that you're using dplyr and ggplot2 rather than base R. Outside of this project, you may find that you prefer using base R functions for certain tasks, and that's just fine! But part of this project is for you to practice the tools we learned in class, which is dplyr and ggplot2.

**Summarizing:**

1.  Compute the *range*, *mean*, and *two other summary statistics* of **one numerical variable** across the groups of **one categorical variable** from your data.
2.  Compute the number of observations for at least one of your categorical variables. Do not use the function `table()`!
3.  Create a categorical variable with 3 or more groups from an existing numerical variable. You can use this new variable in the other tasks! *An example: age in years into "child, teen, adult, senior".*
4. Compute the proportion and counts in each category of one categorical variable across the groups of another categorical variable from your data. Do not use the function `table()`!

**Graphing:**

6. Create a graph of your choosing, make one of the axes logarithmic, and format the axes labels so that they are "pretty" or easier to read.
7. Make a graph where it makes sense to customize the alpha transparency.

Using variables and/or tables you made in one of the "Summarizing" tasks: 

8. Create a graph that has at least two geom layers. 
9. Create 3 histograms, with each histogram having different sized bins. Pick the "best" one and explain why it is the best.

Make sure it's clear what research question you are doing each operation for!

<!------------------------- Start your work below ----------------------------->

**Research Question 1:** What is the relationship between the diameter
and their height_range_id in the dataset?

**Option1 (summarizing)**
I compute the *range*, *mean*, and *median* and *std* of the diameter across the groups of height_range_id from the data. Based on the diameter_summary tibble, it seems there is a positive relationship between height_range_id and diameter_mean and diameter_median. This information indicates that a tree with a larger height_range_id tends to have a larger diameter.

```{r}
diameter_summary<- vancouver_trees %>%
  group_by(height_range_id) %>%
  summarize(
    # compute range
    d_range = diff(range(diameter)),
    # compute mean
    d_mean = mean(diameter),
    # compute median
    d_median = median(diameter),
    #compute std
    d_std = sd(diameter)
  )
print(diameter_summary)
```

**Option7 (graphing)**
I graphed a density plot for diameter versus height_range_id, the different height_range_id are shown as fills. The alpha value is customed to be 0.5 since the transparency matters here. Based on the density plot generated below, we can see a clear relationship between the density and diameter of the trees as well as the height_range_id. It seems like for most cases, as the tree diameter increases, the density of the tree increases as well. Meanwhile, it seems like there is also a positive relationship between the tree diameter and the height_range_id. When the tree diameter is larger, the corresponding height_range_id is also larger. I compute the *range*, *mean*, and *median* and *std* of the diameter across the groups of height_range_id from the data. Based on the diameter_summary tibble, it seems there is a positive relationship between height_range_id and diameter_mean and diameter_median. This information indicates that a tree with a larger height_range_id tends to have a larger diameter.

```{r}
filtered_dataset <- vancouver_trees %>%
  # filter out the diameter > 0
  filter(diameter > 0)

# create a density plot for diameter versus height_range_id
ggplot(data = filtered_dataset, aes(x = diameter)) +
  # customized the alpha value
  geom_density(aes(fill = factor(height_range_id)), alpha = 0.5) +
  labs(
    title = "Density of diameter for different height range id",
    x = "Tree diameter",
    y = "Density"
  ) + scale_x_log10() + theme_minimal()
```

**Research Question 2:** Are certain tree species more prevalent in specific neighborhoods of Vancouver? In other words, are there any relationships between species_name and neighborhood_name?

**Option4 (summarizing)**
I compute the proportion and total_counts in each category of neighbourhood_name across the groups of species_name from the dataset in a tibble called species_in_neighborhood. With this tibble, I know the total and proportion of each species in the corresponding neighborhood, which is useful for the analysis of my research question.

```{r}
species_in_neighborhood <- vancouver_trees %>%
  count(neighbourhood_name, species_name) %>%
  group_by(neighbourhood_name) %>%
  # add column total_count and proportion
  mutate(total_count = sum(n),proportion = n / total_count) %>%
  # set tibble to original state
  ungroup()

head(species_in_neighborhood)
```

**Option6 (graphing)**
I get the most popular species from the above tibble. Then I create a graph of the most prevalent tree species in each neighborhood, x-axis is the proportion and is made logarithmic, y-axis is the neighborhood name. Species_name is the fill. Based on the plot generated, it seems like DOWNTOWN has obvious favors over Rubrum, as well as the FAIRVIEW. STRATHCONA seems to be the only neighborhood that favors the SYLVATICA. PLATANOIDES and SERRULATA seem to be the favorite tree species for most neighborhood districts.

```{r}
most_popular_species <- species_in_neighborhood %>%
  group_by(neighbourhood_name) %>%
  # get the most popular species
  slice_max(order_by = proportion)

 # in order to see the full tibble
options(dplyr.print_min = 100) 
print(most_popular_species)

ggplot(most_popular_species, aes(x = proportion, y = reorder(neighbourhood_name, -proportion), fill = species_name))+
  geom_bar(stat = "identity") +
  labs(
    title = "Most Prevalent Tree Species in Each Neighborhood",
    x = "Proportion",
    y = "Neighborhood name",
    fill = "Species name") + 
  # scale the x axis to log
  scale_x_log10() + 
  theme_minimal()+ 
  # format the labels as percentages
  scale_x_continuous(labels = scales::percent_format(scale = 1))
```

**Research Question 3:** What is the change of tree population in Vancouver changed over time? In other words, the change in the amount of trees planted each year.

Since the two variables in this research question are date_planted (date) and the total number of trees(numerical), it is quite difficult to choose one summary task since all four somehow relate to categorical variables except option 3. In order to make the data analysis close to my research question, I chose to create a categorical variable year_range with 4 groups from the date variable based on extracting the year information from the date variable instead of a numerical variable. 

**Option3 (summarizing)**

```{r}
vancouver_trees <- vancouver_trees %>%
  #split year into 4 categories
  mutate(year_range = case_when( 
    year(date_planted) < 2000 ~ "Before 2000",
    year(date_planted) >= 2000 & year(date_planted) <= 2010 ~ "2000-2010",
    year(date_planted) > 2010 & year(date_planted) <= 2020 ~ "2010-2020",
    TRUE ~ "After 2020"
  ))
glimpse(vancouver_trees)
```

```{r}
vancouver_trees <-vancouver_trees %>%
  #create a new col year_planted through the data variable
  mutate(year_planted = year(date_planted))

# group the data by year 
tree_counts_by_year <- vancouver_trees %>%
  group_by(year_planted) %>%
  
  #count the total number of trees planted each year
  summarise(total_tree_count = n()) %>%
  # set tibble to original state
  ungroup()
print(tree_counts_by_year)
```

**Option6 (graphing)**
Create a graph of the total Number of trees planted over years, y-axes is made logarithmic (total number of tree planted), and format the axes labels.
```{r}
# visualize the change in the amount of trees over years
ggplot(tree_counts_by_year, aes(x = year_planted, y = total_tree_count)) +
  geom_line() +
  # Set the y-axis to be logarithmic
  scale_y_log10() + 
  labs(
    title = "Change in Total Tree Population Over Time",
    x = "Year",
    y = "Total Number of Trees Planted"
  ) +
  theme_minimal() +
  scale_x_continuous(labels = scales::comma)
```

**Research Question 4:** What is a change in the tree density of the top 5 most popular tree species in DOWNTOWN area from 2013 to 2019? 

**Option2 (summarizing)**
I calculate the number of observations for one of the categorical variables, neighborhood_name, and store it as neighbourhood_count. Since this research question is about the tree density of the top 5 most popular tree species in the DOWNTOWN area, it is useful to get a tibble that contains the total amount of trees planted for each neighborhood, which contains the information of DOWNTOWN. Based on the output tibble, it seems like a large of amount of trees were planted in the RENFREW-COLLINGWOOD, KENSINGTON-CEDAR COTTAGE, and HASTINGS-SUNRISE neighborhoods. DOWNTOWN has a round 5000, which is not bad. 

```{r}
# calculate the number of observations for each neighbourhood
neighbourhood_count<- vancouver_trees %>%
  group_by(neighbourhood_name) %>%
  # get the number of tree planted in each neighborhood
  summarise(observations = n()) %>%
  # set tibble to original state
  ungroup()

print(neighbourhood_count)
```

**Option7 (graphing)**
In order to further analyze the research question, I chose to filter out the DOWNTOWN area among all the neighborhoods, and I picked out the top 5 popular tree species based on the n variable for each species. Top 5 tree species in DOWNTOWN are "RUBRUM", "PLATANOIDES", "FREEMANI   X", "SYLVATICA", "BETULUS" respectively.

```{r}
# find the top 5 most popular species in downtown first
# species_in_neighborhood tibble was created above
species_in_downtown <- species_in_neighborhood %>%
  filter(neighbourhood_name == "DOWNTOWN") 
  
print(species_in_downtown)
```
Therefore, I can graph the density plot of the top 5 most popular tree species in the DOWNTOWN area from 2013 to 2019. I adjust the alpha value to 0.4 since transparency matters here. With a smaller alpha value, I am able to see the change in the amount of trees planted over these years for different tree species. Based on the generated plot, it seems like the DOWNTOWN area started to plant a large amount of "PLATANOIDES" in 2017, whereas the amount of "RUBRUM" planted started to drop. The overall trend of planting "BETULUS" was also an up-trend and the overall trend of "FREEMANI   X" was a down-trend. It might be due to the change in climate conditions so that certain tree species would become more popular in certain districts.

```{r}
# filter the dataset for the downtown neighborhood and the top 5 popular species
downtown_species <- vancouver_trees %>%
  filter(neighbourhood_name == "DOWNTOWN" & 
         year_planted >= 2013 & year_planted <= 2019 & 
         species_name %in% c("RUBRUM", "PLATANOIDES","FREEMANI   X", "SYLVATICA", "BETULUS"))

# create a density plot with personalized alpha value
ggplot(data = downtown_species, aes(x = year_planted, fill = species_name)) +
  geom_density(alpha = 0.4) +
  labs(
    title = "Density of the top 5 species in DOWNTOWN from 2013 to 2019",
    x = "Year",
    y = "Density"
  ) + 
  theme_minimal()
```
<!----------------------------------------------------------------------------->

### 1.3 (2 points)

Based on the operations that you've completed, how much closer are you to answering your research questions? Think about what aspects of your research questions remain unclear. Can your research questions be refined, now that you've investigated your data a bit more? Which research questions are yielding interesting results?

<!------------------------- Write your answer here ---------------------------->
Based on the above operations, I think my data analysis outputs relevant results to all the research questions. Research Question 1 is yielding useful results, it shows a positive relationship between height_range_id diameter_mean and diameter_median. This information indicates that a tree with a larger height_range_id tends to have a larger diameter. The generated further proved this result.

Meanwhile, Research Question 2 yields interesting results. Based on the generated plot, it is clear to see that each neighborhood has its favorite tree species. For example, downtown favors Rubrum the most, the proportion is almost 20% in the downtown area. Fairview also plants this kind of tree the most, occupying about 14% of the trees in that neighborhood. STRATHCONA seems to be the only neighborhood that favors the SYLVATICA tree species. PLATANOIDES and SERRULATA look like the favorite tree species for most neighborhood districts.

At the same time, Research Question 3 is yielding meaningful results. I plotted the total amount of trees planted over the years. it is clear to see from the plot that there is an increasing trend of tree planting plans starting from around 1990 to 1995, after that, there's no obvious increasing trend anymore. Whereas starting from the year 2013, the total amount of trees planted in Vancouver per year started to decrease. Therefore, I think these data analysis results are useful in urban planning, which indicates that the government should increase the total amount of trees planted every year.

Lastly, Research Question 4 shows the top 5 most popular tree species in the DOWNTOWN area from 2013 to 2019 through a density plot. With personalized lower alpha value, I was able to see the change in the amount of trees planted over these years for different tree species. The graph shows that the DOWNTOWN area started to plant a large amount of "PLATANOIDES" in 2017, whereas the amount of "RUBRUM" planted started to drop. More detailed observations are included in the above section. 

<!----------------------------------------------------------------------------->

# Task 2: Tidy your data 

In this task, we will do several exercises to reshape our data. The goal here is to understand how to do this reshaping with the `tidyr` package.

A reminder of the definition of *tidy* data:

-   Each row is an **observation**
-   Each column is a **variable**
-   Each cell is a **value**

### 2.1 (2 points)

Based on the definition above, can you identify if your data is tidy or untidy? Go through all your columns, or if you have \>8 variables, just pick 8, and explain whether the data is untidy or tidy.

<!--------------------------- Start your work below --------------------------->
From the glimpse() function, each row represents a tree observation, and each column corresponds to a specific variable.It seems quite tidy from thi aspect.
```{r}
glimpse(vancouver_trees)
```
However, based on the results, the vancouver_trees dataset contains missing values in certain columns, so it is untidy.
```{r}
missing_value <- sum(is.na(vancouver_trees))
if (missing_value > 0) {
  cat("Missing values exist! The dataset is untidy")
} else {
  cat("No missing values found!")
}
```

<!----------------------------------------------------------------------------->

### 2.2 (4 points)

Now, if your data is tidy, untidy it! Then, tidy it back to it's original state.

If your data is untidy, then tidy it! Then, untidy it back to it's original state.

Be sure to explain your reasoning for this task. Show us the "before" and "after".

<!--------------------------- Start your work below --------------------------->

**1.** Since my data is untidy, I will tidy the data. Before the task, the dataset is untidy as shown by the prompt message

```{r}
# check for missing values in the entire dataset
missing_value <- sum(is.na(vancouver_trees))
if (missing_value > 0) {
  cat("Missing values exist! The dataset is untidy")
} else {
  cat("No missing values found!")
}
```

```{r}
# check the NA columns
NA_columns <- vancouver_trees %>%
  summarise_all(~sum(is.na(.))) %>%
  as.logical()

# get the variable names with missing values
names(vancouver_trees)[NA_columns]

#keep a copy of the original untidy daataset
vancouver_trees_cpy <- vancouver_trees

# remove the rows with missing values in these columns
vancouver_trees <- vancouver_trees %>%
  drop_na(cultivar_name, plant_area, date_planted, longitude, latitude, year_planted)
```
**2.** After tidying the data using tidyr package, check whether there is NA values now. It looks great, no missing values found in all columns.

```{r}
#check again
missing_value <- sum(is.na(vancouver_trees))
if (missing_value > 0) {
  cat("Missing values exist! The dataset is untidy")
} else {
  cat("No missing values found!")
}
```
**3.** Set the dataset back to its original state

```{r}
vancouver_trees <-vancouver_trees_cpy
#check that the dataset is the original one
missing_value <- sum(is.na(vancouver_trees))
if (missing_value > 0) {
  cat("Missing values exist! The dataset is untidy")
} else {
  cat("No missing values found!")
}
```

<!----------------------------------------------------------------------------->

### 2.3 (4 points)

Now, you should be more familiar with your data, and also have made progress in answering your research questions. Based on your interest, and your analyses, pick 2 of the 4 research questions to continue your analysis in the remaining tasks:

<!-------------------------- Start your work below ---------------------------->
I pick the Research Question 3 and 4 in Task 1

**1.** Are certain tree species more prevalent in
specific neighborhoods of Vancouver? In other words, is there any
relationships between species_name and neighborhood_name?

**2.** What is the change of tree population in
Vancouver changed over time? In other words, the change of amount of the tree planted each year.

<!----------------------------------------------------------------------------->

Explain your decision for choosing the above two research questions.

<!--------------------------- Start your work below --------------------------->
**1.** As described before, this research question achieved interesting results. There relationship between species_name and neighbourhood_name exists. I think further possible analysis can be what is the most popular tree species in the whole Vancouver area?

**2.** This research question is meaningful in terms of urban planning since the decrease in the amount of trees planted each year tells us that more trees definitely need to be planted in the future. Further analysis can discover whether there has been a decrease in planting some specific kinds of trees over these years. What are some possible reasons for that?
<!----------------------------------------------------------------------------->

Now, try to choose a version of your data that you think will be appropriate to answer these 2 questions. Use between 4 and 8 functions that we've covered so far (i.e. by filtering, cleaning, tidy'ing, dropping irrelevant columns, etc.).

(If it makes more sense, then you can make/pick two versions of your data, one for each research question.) 

**1.** The suitable data is species_in_neighborhood dataset. From the results generated below, SERRULATA has a count of 13357, which is the most popular tree species in Vancouver, followed by CERASIFERA and PLATANOIDES, which has 12031 and 11963 planted trees respectively.
```{r}
#Dataset for Q1
species_in_neighborhood <- vancouver_trees %>%
  count(neighbourhood_name, species_name) %>%
  group_by(neighbourhood_name) %>%
  mutate(total_count = sum(n),proportion = n / total_count) %>%
  ungroup()
glimpse(species_in_neighborhood)

# calculate the total amount of each species in Vancouver area
overall_species_counts <- species_in_neighborhood %>%
  group_by(species_name) %>%
  summarize(total_count = sum(n)) %>%
  arrange(desc(total_count)) %>%
  ungroup()

print(overall_species_counts)
```

**2.** The suitable dataset is vancouver_trees_filter since I need to filter out the year from 2013 to 2019 from th column year_planted. Meanwhile, I need to use the species_name columns. As the results shown, over the period of 2013 and 2019, it seems like the popular tree species,SERRULATA and CERASIFERA have a decrease in planting as well as the RUBRUM. It may relate to some shifts and changes in urban plannings or the change in climate factors.

```{r}
# filter the dataset to select year between 2013 and 2019
vancouver_trees_filter <- vancouver_trees %>%
  filter(year_planted >= 2013, year_planted <= 2019)


species_counts <- vancouver_trees_filter %>%
  # group by the species and year 
  group_by(species_name, year_planted) %>%
  # count the number of trees planted
  summarize(total_tree = n()) %>%
  ungroup()

# create separate columns for each year
wide_version <- species_counts %>%
  pivot_wider(names_from = year_planted, values_from = total_tree)

# calculate the difference between 2013 and 2019
wide_version <- wide_version %>%
  mutate(drop_amount = `2019` - `2013`)

# select those species that decrease
decrease_species <- wide_version %>%
  filter(drop_amount < 0) %>%
  select(species_name, drop_amount)

# show results starting from the species that drops the most
decrease_species <- decrease_species %>%
  arrange(drop_amount)

decrease_species
```
<!--------------------------- Start your work below --------------------------->

# Task 3: Modelling

## 3.0 (no points)

Pick a research question from 1.2, and pick a variable of interest (we'll call it "Y") that's relevant to the research question. Indicate these.

<!-------------------------- Start your work below ---------------------------->

**Research Question**: FILL_THIS_IN

**Variable of interest**: FILL_THIS_IN

<!----------------------------------------------------------------------------->

## 3.1 (3 points)

Fit a model or run a hypothesis test that provides insight on this variable with respect to the research question. Store the model object as a variable, and print its output to screen. We'll omit having to justify your choice, because we don't expect you to know about model specifics in STAT 545.

-   **Note**: It's OK if you don't know how these models/tests work. Here are some examples of things you can do here, but the sky's the limit.

    -   You could fit a model that makes predictions on Y using another variable, by using the `lm()` function.
    -   You could test whether the mean of Y equals 0 using `t.test()`, or maybe the mean across two groups are different using `t.test()`, or maybe the mean across multiple groups are different using `anova()` (you may have to pivot your data for the latter two).
    -   You could use `lm()` to test for significance of regression coefficients.

<!-------------------------- Start your work below ---------------------------->

<!----------------------------------------------------------------------------->

## 3.2 (3 points)

Produce something relevant from your fitted model: either predictions on Y, or a single value like a regression coefficient or a p-value.

-   Be sure to indicate in writing what you chose to produce.
-   Your code should either output a tibble (in which case you should indicate the column that contains the thing you're looking for), or the thing you're looking for itself.
-   Obtain your results using the `broom` package if possible. If your model is not compatible with the broom function you're needing, then you can obtain your results by some other means, but first indicate which broom function is not compatible.

<!-------------------------- Start your work below ---------------------------->

<!----------------------------------------------------------------------------->

# Task 4: Reading and writing data

Get set up for this exercise by making a folder called `output` in the top level of your project folder / repository. You'll be saving things there.

## 4.1 (3 points)

Take a summary table that you made from Task 1, and write it as a csv file in your `output` folder. Use the `here::here()` function.

-   **Robustness criteria**: You should be able to move your Mini Project repository / project folder to some other location on your computer, or move this very Rmd file to another location within your project repository / folder, and your code should still work.
-   **Reproducibility criteria**: You should be able to delete the csv file, and remake it simply by knitting this Rmd file.

<!-------------------------- Start your work below ---------------------------->

<!----------------------------------------------------------------------------->

## 4.2 (3 points)

Write your model object from Task 3 to an R binary file (an RDS), and load it again. Be sure to save the binary file in your `output` folder. Use the functions `saveRDS()` and `readRDS()`.

-   The same robustness and reproducibility criteria as in 4.1 apply here.

<!-------------------------- Start your work below ---------------------------->

<!----------------------------------------------------------------------------->

# Overall Reproducibility/Cleanliness/Coherence Checklist 

Here are the criteria we're looking for.

## Coherence (0.5 points)

The document should read sensibly from top to bottom, with no major continuity errors. 

The README file should still satisfy the criteria from the last milestone, i.e. it has been updated to match the changes to the repository made in this milestone. 

## File and folder structure (1 points)

You should have at least three folders in the top level of your repository: one for each milestone, and one output folder. If there are any other folders, these are explained in the main README.

Each milestone document is contained in its respective folder, and nowhere else.

Every level-1 folder (that is, the ones stored in the top level, like "Milestone1" and "output") has a `README` file, explaining in a sentence or two what is in the folder, in plain language (it's enough to say something like "This folder contains the source for Milestone 1").

## Output (1 point)

All output is recent and relevant:

-   All Rmd files have been `knit`ted to their output md files. 
-   All knitted md files are viewable without errors on Github. Examples of errors: Missing plots, "Sorry about that, but we can't show files that are this big right now" messages, error messages from broken R code
-   All of these output files are up-to-date -- that is, they haven't fallen behind after the source (Rmd) files have been updated.
-   There should be no relic output files. For example, if you were knitting an Rmd to html, but then changed the output to be only a markdown file, then the html file is a relic and should be deleted.

Our recommendation: delete all output files, and re-knit each milestone's Rmd file, so that everything is up to date and relevant.

## Tagged release (0.5 point)

You've tagged a release for Milestone 2. 

### Attribution

Thanks to Victor Yuan for mostly putting this together.