---
title: "Mini Data-Analysis Deliverable 1"
output: github_document
---

# Welcome to your (maybe) first-ever data analysis project!

And hopefully the first of many. Let's get started:

1.  Install the [`datateachr`](https://github.com/UBC-MDS/datateachr) package by typing the following into your **R terminal**:

<!-- -->

    install.packages("devtools")
    devtools::install_github("UBC-MDS/datateachr")

2.  Load the packages below.

```{r}
library(datateachr)
library(tidyverse)
```

3.  Make a repository in the <https://github.com/stat545ubc-2023> Organization. You can do this by following the steps found on canvas in the entry called [MDA: Create a repository](https://canvas.ubc.ca/courses/126199/pages/mda-create-a-repository). One completed, your repository should automatically be listed as part of the stat545ubc-2023 Organization.

# Instructions

## For Both Milestones

-   Each milestone has explicit tasks. Tasks that are more challenging will often be allocated more points.

-  Each milestone will be also graded for reproducibility, cleanliness, and coherence of the overall Github submission. 

- While the two milestones will be submitted as independent deliverables, the analysis itself is a continuum - think of it as two chapters to a story. Each chapter, or in this case, portion of your analysis, should be easily followed through by someone unfamiliar with the content. [Here](https://swcarpentry.github.io/r-novice-inflammation/06-best-practices-R/) is a good resource for what constitutes "good code". Learning good coding practices early in your career will save you hassle later on!

- The milestones will be equally weighted. 

## For Milestone 1

**To complete this milestone**, edit [this very `.Rmd` file](https://raw.githubusercontent.com/UBC-STAT/stat545.stat.ubc.ca/master/content/mini-project/mini-project-1.Rmd) directly. Fill in the sections that are tagged with `<!--- start your work below --->`.

**To submit this milestone**, make sure to knit this `.Rmd` file to an `.md` file by changing the YAML output settings from `output: html_document` to `output: github_document`. Commit and push all of your work to the mini-analysis GitHub repository you made earlier, and tag a release on GitHub. Then, submit a link to your tagged release on canvas.

**Points**: This milestone is worth 36 points: 30 for your analysis, and 6 for overall reproducibility, cleanliness, and coherence of the Github submission. 

# Learning Objectives

By the end of this milestone, you should:

-   Become familiar with your dataset of choosing
-   Select 4 questions that you would like to answer with your data
-   Generate a reproducible and clear report using R Markdown
-   Become familiar with manipulating and summarizing your data in tibbles using `dplyr`, with a research question in mind.

# Task 1: Choose your favorite dataset 

The `datateachr` package by Hayley Boyce and Jordan Bourak currently composed of 7 semi-tidy datasets for educational purposes. Here is a brief description of each dataset:

-   *apt_buildings*: Acquired courtesy of The City of Toronto's Open Data Portal. It currently has 3455 rows and 37 columns.

-   *building_permits*: Acquired courtesy of The City of Vancouver's Open Data Portal. It currently has 20680 rows and 14 columns.

-   *cancer_sample*: Acquired courtesy of UCI Machine Learning Repository. It currently has 569 rows and 32 columns.

-   *flow_sample*: Acquired courtesy of The Government of Canada's Historical Hydrometric Database. It currently has 218 rows and 7 columns.

-   *parking_meters*: Acquired courtesy of The City of Vancouver's Open Data Portal. It currently has 10032 rows and 22 columns.

-   *steam_games*: Acquired courtesy of Kaggle. It currently has 40833 rows and 21 columns.

-   *vancouver_trees*: Acquired courtesy of The City of Vancouver's Open Data Portal. It currently has 146611 rows and 20 columns.

**Things to keep in mind**

-   We hope that this project will serve as practice for carrying our your own *independent* data analysis. Remember to comment your code, be explicit about what you are doing, and write notes in this markdown document when you feel that context is required. As you advance in the project, prompts and hints to do this will be diminished - it'll be up to you!

-   Before choosing a dataset, you should always keep in mind **your goal**, or in other ways, *what you wish to achieve with this data*. This mini data-analysis project focuses on *data wrangling*, *tidying*, and *visualization*. In short, it's a way for you to get your feet wet with exploring data on your own.

And that is exactly the first thing that you will do!

1.1 **(1 point)** Out of the 7 datasets available in the `datateachr` package, choose **4** that appeal to you based on their description. Write your choices below:

**Note**: We encourage you to use the ones in the `datateachr` package, but if you have a dataset that you'd really like to use, you can include it here. But, please check with a member of the teaching team to see whether the dataset is of appropriate complexity. Also, include a **brief** description of the dataset here to help the teaching team understand your data.

<!-------------------------- Start your work below ---------------------------->

1: apt_buildings 

2: building_permits

3: cancer_sample

4: vancouver_trees

<!----------------------------------------------------------------------------->

1.2 **(6 points)** One way to narrowing down your selection is to *explore* the datasets. Use your knowledge of dplyr to find out at least *3* attributes about each of these datasets (an attribute is something such as number of rows, variables, class type...). The goal here is to have an idea of *what the data looks like*.

*Hint:* This is one of those times when you should think about the cleanliness of your analysis. I added a single code chunk for you below, but do you want to use more than one? Would you like to write more comments outside of the code chunk?

<!-------------------------- Start your work below ---------------------------->
### Exploration for apt_buildings dataset:
  * **Number of rows and columns (size):** apt_buildings dataset has 3455 rows, 37 column variables, which means it is a fairly large dataset.
  * **Data types:** Most columns are of the type character (chr), but there are also some columns with numeric data types (dbl).
  * **Missing values:** Some columns like amenities contains NA values, which indicates we might need to tidy the dataset.
  * **Binary variables:** Some columns like locker_or_storage_room and laundry_room seem to have binary variable type, which means the values of the columns are simply YES or NO. 
  * **Categorical variables:** Some columns like heating_type and property_type may represent categorical variables with different levels. 
```{r}
### EXPLORE HERE ###
glimpse(apt_buildings)
apt_buildings

```

### Exploration for building_permits dataset:
  * **Number of rows and columns (size):** building_permits dataset has 20680 rows, 14 column variables
  * **Data types:** Most columns are of the type character (chr), but there are also some columns with numeric data types (dbl). There is a column "issue_date" is of the type (date), which contains data information.
  * **Missing values:** Some columns like project_description and building_contractor contains NA values, which indicates we might need to tidy the dataset.
  * **Categorical variables:** Some columns like type_of_work may represent categorical variables with different levels. The dataset does not seem to have any binary variables.

```{r}
### EXPLORE HERE ###
glimpse(building_permits)
```

### Exploration for cancer_sample dataset:
  * **Number of rows and columns (size):** cancer_sample dataset has 569 rows, 32 column variables, compares to the previous dataset, this dataset is fairly smaller.
  * **Data types:** Most the columns are with numeric data types (dbl). There is only one column "diagnosis" is of the type character (chr).
  * **Missing values:** There is no NA value in the cancer_sample dataset, which means this dataset is pretty tidy!

```{r}
### EXPLORE HERE ###
glimpse(cancer_sample)
if (any(is.na(cancer_sample))) {
  print("NA value exists")
  }else{
    print("NA value does not exist")}
```

### Exploration for vancouver_trees dataset:
  * **Number of rows and columns (size):** vancouver_trees dataset has 146611 rows, 20 column variables, which means it is a very large dataset.
  * **Data types:** Most columns are of the type character (chr), but there are also some columns with numeric data types (dbl). There is a column "date_planted" is of the type (date), which contains date information of when the tree was planted.
  * **Missing values:** Some columns like cultivar_name contains NA values, which indicates we might need to tidy the dataset.

```{r}
### EXPLORE HERE ###
glimpse(vancouver_trees)
vancouver_trees
if (any(is.na(vancouver_trees))){
  print("NA value exists")
  }else{
    print("NA value does not exist")}
```

<!----------------------------------------------------------------------------->

1.3 **(1 point)** Now that you've explored the 4 datasets that you were initially most interested in, let's narrow it down to 1. What lead you to choose this one? Briefly explain your choice below.

<!-------------------------- Start your work below ---------------------------->
**Answer for Question1.3:**
I would choose vancouver_trees dataset. Since although it contains some NA values in some of it's columns so I may need to tidy the dataset, compared to cancer_sample dataset, the variable names are easier to interpret. I think this is very essential in data analysis.It can help me interpret the relationship betwwen variables more easily. Therefore, I think I will choose vancouver_trees dataset.
<!----------------------------------------------------------------------------->

1.4 **(2 points)** Time for a  final decision! Going back to the beginning, it's important to have an *end goal* in mind. For example, if I had chosen the `titanic` dataset for my project, I might've wanted to explore the relationship between survival and other variables. Try to think of 1 research question that you would want to answer with your dataset. Note it down below.

<!-------------------------- Start your work below ---------------------------->
**Answer for Question 1.4:**
In vancouver_trees dataset, the research question that I will have is to explore "What is the relationship between tree species and their assigned status in the dataset?
<!----------------------------------------------------------------------------->

# Important note

Read Tasks 2 and 3 *fully* before starting to complete either of them. Probably also a good point to grab a coffee to get ready for the fun part!

This project is semi-guided, but meant to be *independent*. For this reason, you will complete tasks 2 and 3 below (under the **START HERE** mark) as if you were writing your own exploratory data analysis report, and this guidance never existed! Feel free to add a brief introduction section to your project, format the document with markdown syntax as you deem appropriate, and structure the analysis as you deem appropriate. If you feel lost, you can find a sample data analysis [here](https://www.kaggle.com/headsortails/tidy-titarnic) to have a better idea. However, bear in mind that it is **just an example** and you will not be required to have that level of complexity in your project.

# Task 2: Exploring your dataset 

If we rewind and go back to the learning objectives, you'll see that by the end of this deliverable, you should have formulated *4* research questions about your data that you may want to answer during your project. However, it may be handy to do some more exploration on your dataset of choice before creating these questions - by looking at the data, you may get more ideas. **Before you start this task, read all instructions carefully until you reach START HERE under Task 3**.

2.1 **(12 points)** Complete *4 out of the following 8 exercises* to dive deeper into your data. All datasets are different and therefore, not all of these tasks may make sense for your data - which is why you should only answer *4*. 

Make sure that you're using dplyr and ggplot2 rather than base R for this task. Outside of this project, you may find that you prefer using base R functions for certain tasks, and that's just fine! But part of this project is for you to practice the tools we learned in class, which is dplyr and ggplot2.

1.  Plot the distribution of a numeric variable.
2.  Create a new variable based on other variables in your data (only if it makes sense)
3.  Investigate how many missing values there are per variable. Can you find a way to plot this?
4.  Explore the relationship between 2 variables in a plot.
5.  Filter observations in your data according to your own criteria. Think of what you'd like to explore - again, if this was the `titanic` dataset, I may want to narrow my search down to passengers born in a particular year...
6.  Use a boxplot to look at the frequency of different observations within a single variable. You can do this for more than one variable if you wish!
7.  Make a new tibble with a subset of your data, with variables and observations that you are interested in exploring.
8.  Use a density plot to explore any of your variables (that are suitable for this type of plot).**

2.2 **(4 points)** For each of the 4 exercises that you complete, provide a *brief explanation* of why you chose that exercise in relation to your data (in other words, why does it make sense to do that?), and sufficient comments for a reader to understand your reasoning and code.

<!-------------------------- Start your work below ---------------------------->
### Exercise 1: Plot the distribution of a numeric variable

```{r Exercise1_histogram}
#refer to choice 1 above

# Load library
library(ggplot2)
library(dplyr)

glimpse(vancouver_trees)

# A histogram of Distribution of on_street_block versus the frequency of each street block
ggplot(vancouver_trees, aes(x = on_street_block )) +
  geom_histogram(binwidth = 100, fill = "pink", color="black") +
  #Adding labels on x and y axis
  labs(title = "Distribution of on_street_block ",
       x = "On Street Block Number ",
       y = "Frequency")
```

**Brief Explanation for Exercise 1**

The reason I explore the distribution of on_street_block using a histogram to view the frequency for each street block is that I would like to identifying the street blocks that have a higher concentration of trees. This information is valuable for urban planning and the possible tree maintenance in the future. For example, in urban planning, the tree planting schedule in the street blocks with relatively lower distribution of trees might needed to be prioritized.

### Exercise 2: Investigating missing values and generate plot
```{r Exercise2_missing_values_barchart}
#refer to choice 3 above

# calculate # of missing values for each variable
missingVal <- vancouver_trees %>%
  summarise_all(~ sum(is.na(.)))

# create a tibble with variable and the missing counts
missingValTibble <- tibble(variableName = names(missingVal), missingCount = as.integer(as.vector(missingVal)))

# only include the column with missing value in the x-axis
missingValFiltered <- missingValTibble %>%
  filter(missingCount > 0)

# A bar chart to visualize the counts of missing values for each variable
ggplot(missingValFiltered, aes(x=variableName, y = missingCount)) +
  geom_bar(stat = "identity",fill = "pink", color="black") +
  labs(title = "Missing Value Counts for Certain Variable",
       x = "Variable Name",
       y = "Missing Count")
```

**Brief Explanation for Exercise 2**

This exercise is very important in data analysis since it will help us to identify the quality of the dataset. For example, it can tell us which columns has missing values (NA) so that we preprocess the dataset, it can tell us we should do corresponding data cleaning or imputation. Meanwhile, it can let us know the distribution of missing values for all variables and give us a better insights into the column variables where incomplete information may exist.

### Exercise 3: Make a new tibble with a subset of the data
```{r Exercise3_new_tibble}
# refer to choice 7 above
# create a new tibble with the the following three selected variables
treeSubset <- vancouver_trees %>%
  select(genus_name, species_name, assigned)

# group the tibble by species_name
treeSummary <- treeSubset %>%
  group_by(species_name) %>%
  # add some new variables
  summarize(
    numberTrees = n(),
    assignedCount = sum(assigned == "Y"),
    unassignedCount = sum(assigned == "N")
  )
treeSummary

# arrange the tibble by number of trees in descending order
treeSummary <- treeSummary %>%
  arrange(desc(numberTrees))
treeSummary
```

**Brief Explanation for Exercise 3**

For this exercise, I created a new tibble containing three column variables, "genus_name", "species_name", and "assigned". For the research question above, I would like to know "What is the relationship between tree species and their assigned status in the dataset." This is the main reason I chose to do this exercise. After creating the new tibble, I think I should further look deep into the dataset to see the relationships between these variables. Therefore, I group by species_name and added some new variables. As a result, the total number of trees for each species and the count of trees that are assigned (Y) and unassigned (N) can be shown clearly in the treeSummary tibble.This is useful and it is relate to my research question. From the result, we can clearly know that SERRULATA is the species with the most number of trees

### Exercise 4: Density Plot
```{r Exercise4_density_plot}
# refer to choice 8 above
# Create a density plots to explore whether the root barrier will influence the diameter of trees.

# filter the dataset with diameter larger than 0
filtered_dataset <- vancouver_trees %>%
  filter(diameter > 0)

# create a density plot
ggplot(data = filtered_dataset, aes(x = diameter)) +
  geom_density(aes(fill = root_barrier), alpha = 0.5) +
  #adjust the size
  scale_x_log10() +
  # add title, x and y label to the plot
  labs(title = "Density of Diameter for Different Root barrier",
       x = "Diameter of Tree",
       y = "Desnsity")+
  theme_minimal()
```

**Brief Explanation for Exercise 4**

The density plot generated in this question might be useful in environmental studies. The density plot provides a visual representation of how the root barrier will influence the three diameters in the dataset. The density lot shows that when the diameter of the three is smaller than 10.0, the density of root_barrier (Y) is higher. Whereas when the diameter of the three is larger than 10.0, the density of root_barrier (N) is higher. 
<!----------------------------------------------------------------------------->

# Task 3: Choose research questions 

**(4 points)** So far, you have chosen a dataset and gotten familiar with it through exploring the data. You have also brainstormed one research question that interested you (Task 1.4).  Now it's time to pick 4 research questions that you would like to explore in Milestone 2! Write the 4 questions and any additional comments below. 

<!--- *****START HERE***** --->
**Research Question 1:** How does the density of trees vary with the corresponding latitude and longitude coordinates in the dataset?

**Research Question 2:** What is the relationship between the diameter and their heiht_range_id in the dataset?

**Research Question 3:** Are certain tree species more prevalent in specific neighborhoods of Vancouver? In other words, is there any relationships between species_name and neighborhood_name?

**Research Question 4:** What is the change of tree population in Vancouver changed over time in terms of the type of species?
<!----------------------------->

# Overall reproducibility/Cleanliness/Coherence Checklist 

## Coherence (0.5 points)

The document should read sensibly from top to bottom, with no major continuity errors. An example of a major continuity error is having a data set listed for Task 3 that is not part of one of the data sets listed in Task 1. 

## Error-free code (3 points) 

For full marks, all code in the document should run without error. 1 point deduction if most code runs without error, and 2 points deduction if more than 50% of the code throws an error. 

## Main README (1 point)

There should be a file named `README.md` at the top level of your repository. Its contents should automatically appear when you visit the repository on GitHub.

Minimum contents of the README file:

-   In a sentence or two, explains what this repository is, so that future-you or someone else stumbling on your repository can be oriented to the repository.
-   In a sentence or two (or more??), briefly explains how to engage with the repository. You can assume the person reading knows the material from STAT 545A. Basically, if a visitor to your repository wants to explore your project, what should they know?

Once you get in the habit of making README files, and seeing more README files in other projects, you'll wonder how you ever got by without them! They are tremendously helpful.

## Output (1 point)

All output is readable, recent and relevant:

-   All Rmd files have been `knit`ted to their output md files. 
-   All knitted md files are viewable without errors on Github. Examples of errors: Missing plots, "Sorry about that, but we can't show files that are this big right now" messages, error messages from broken R code
-   All of these output files are up-to-date -- that is, they haven't fallen behind after the source (Rmd) files have been updated.
-   There should be no relic output files. For example, if you were knitting an Rmd to html, but then changed the output to be only a markdown file, then the html file is a relic and should be deleted.

(0.5 point deduction if any of the above criteria are not met. 1 point deduction if most or all of the above criteria are not met.)

Our recommendation: right before submission, delete all output files, and re-knit each milestone's Rmd file, so that everything is up to date and relevant. Then, after your final commit and push to Github, CHECK on Github to make sure that everything looks the way you intended!

## Tagged release (0.5 points)

You've tagged a release for Milestone 1. 

### Attribution

Thanks to Icíar Fernández Boyano for mostly putting this together, and Vincenzo Coia for launching.